Dominance Regions for Rank Two Cluster Algebras

### 2022-04-03 dominance_regions.tex
Committing to pull

          \item If $\lambda_1 > 0$, $\lambda_1+b\lambda_2 < 0$, and $-c\lambda_1-(bc-1)\lambda_2\le 0$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $\big((bc-1)\lambda_1+(b^2c-2b)\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$.

>>>>

          \item If $\lambda_1 > 0$, $\lambda_1+b\lambda_2 < 0$, and $-c\lambda_1-(bc-1)\lambda_2\le 0$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $\big((bc-1)\lambda_1+b^2c\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$.
